---
title: "korea"
author: "Amy Fox"
date: "2025-06-25"
output: html_document
---

Download .fit data from connect.Garmin.com

Additional things to try
 - add in points in the cities where we spent the night
 - see if I can show the speed as the color on the graph
 - could try a shiny app and click on the different days to show more information about it like total distance, avg speed, ascent/descent
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE) 
```

Install package from github that converts FIT files to df
```{r}
# if(!requireNamespace("remotes")) {
#     install.packages("remotes")
# }
# remotes::install_github("grimbough/FITfileR")
```

```{r}
library(FITfileR)
library(dplyr)
library(leaflet)
```


```{r}
# test with one example
df1 <- readFitFile("./data/korea/15870474757_ACTIVITY.fit") %>%
    records() %>%
  bind_rows() %>%
  arrange(timestamp) %>%
  filter(position_lat < 179.9 & position_long < 179.9) # remove when gps still locating..

```



```{r}
fit_folder <- "./data/korea"
fit_files <- list.files(fit_folder, pattern = "\\.fit$", full.names = TRUE)

# read data from .fit file
get_fit_gps <- function(file) {
  df <- readFitFile(file) %>%
    records() %>%
    bind_rows() %>%
    filter(position_lat < 179.9 & position_long < 179.9) 
  
  return(df)
}

# combine all GPS data
all_gps_data <- lapply(fit_files, get_fit_gps) %>%
  bind_rows() %>%
  arrange(timestamp)
```

Find position of where we stopped for the night each night

I want this to ultimately say something like "Day 1: city name"
```{r}

clean_gps <- all_gps_data %>%
  mutate(new_date = as.Date(timestamp),
         time = strftime(timestamp, format="%H:%M:%S"),
         day_number = dense_rank(new_date),
         day_label = paste("Day", day_number)) %>%
  group_by(new_date) %>%
  mutate(stops = case_when(time == max(time) ~ "Stop",
                           TRUE ~"Bike"
                           )) %>%
  ungroup()


```


Print out leaflet track
```{r}
leaflet(  ) %>%
  addTiles() %>%
  addPolylines(data = clean_gps,
               lng = ~position_long,
               lat = ~position_lat) %>%
  addMarkers(data = clean_gps %>%
                filter(stops == "Stop"),
            lat = ~position_lat,
            lng = ~position_long,
  label = clean_gps$day_label
    )
```


```{r}
all_gps_data %>%
  head()
```

